---
title: "hugo"
author: "Jameson Quinn"
date: "May 5, 2015"
output: ioslides_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}

library(data.table)
library(ggplot2)
library(boot)
library(elasticnet)
library(plyr)
library(stringdist)

cats = c("1 - novel", "2 - novella", "3 - novelette", "4 - short story", 
"5 - non-fiction book", "6 - dramatic presentation", "7 - pro editor", 
"8 - pro artist", "9 - semiprozine", "10 - fanzine", "11 - fan writer", 
"12 - fan artist", "13 -  Campbell Award (not a Hugo)")
hugos = data.table(read.fwf("catsort.txt",widths = c(5,3,9,9,76-27,2,113-78,99),comment.char="", strip.white=T))
setnames(hugos,c("voter","cat","postdate","gotdate","title","numvotes","author","publisher"))
hugos[,title:=as.character(title)]
titles = c()
for (i in 1:dim(hugos)[1]) {
  title = hugos[i,title]
  titdist = stringdist(titles, title, method="jw")
  if (all(!is.finite(titdist))) {
    titdist = rep(1,length(titdist))
  }
  if (hugos[i,cat] < 7) {
    cutoff = 0.13
  } else {
    cutoff = 0.09
  }
  if (min(titdist) > cutoff) {
    titles = c(titles,title)
    titdist = c(titdist,0)
  } else if (min(titdist) > (cutoff / 2)) {
    cat(hugos[i,cat],min(titdist),title,titles[which(titdist == min(titdist))[1]],"\n")
  }
  
  hugos[i,titindex:=  which(titdist == min(titdist))[1]]
  if (i %% 1000 == 0) {
    print(i)
    print("....")
    }
}

novels = hugos[cat==1]
titles[novels[,.N,by=titindex][order(-N)][1:5,titindex]]
for (i in 1:13) {cat("Category",cats[i],"- had",sum(count(hugos[cat==i,][,.N,by=titindex][,N])[-1:-3,2]),"works with 3 or more votes.\n")}
sdvlpe = function(ballots, allValid = T) {
  #count raw votes
  if (!("rawvotes" %in% names(ballots))) {
    ballots[,rawvotes:=.N,by=titindex]
  }
  
  #find plurality winners
  rawOrder = ballots[,.N,by=titindex][order(-N)]
  nwin = 5
  while (rawOrder[nwin,N] == rawOrder[nwin+1,N]) {
    nwin = nwin + 1
  }
  rawWinners = sort(rawOrder[1:nwin,titindex])
  
  #find SDVLPE winners
  if (allValid) {
    ballots[,valid:=T]
  }
  done=F
  #Mass elimination
  ballots[valid==T,fvotes:=1/.N,by=voter]
  fvotes = ballots[,list(f=sum(fvotes),raw=rawvotes[1]),by=titindex][order(-f)]
  cutoff = fvotes[5,f]
  ballots[rawvotes < cutoff, valid:=F]
  
  ties = c()
  allFs = data.table()
  strange = F
  round = 0
  while (!done) {
    round = round + 1
    ballots[valid==T,fvotes:=1/.N,by=voter]
    fvotes = ballots[valid==T,list(f=sum(fvotes),raw=rawvotes[1],r =round),by=titindex][order(f)]
    allFs = rbind(allFs,fvotes)
    njoust = 2
    numcand = dim(fvotes)[1]
    while ((njoust < numcand) & (fvotes[njoust,f] == fvotes[njoust+1,f])) {
      njoust = njoust + 1
    }
    #print(fvotes)
    losers = fvotes[1:njoust]
    losers = losers[raw == min(losers[,raw]), titindex]
    #print(losers)
    if (length(losers) > 1) {
      losers = allFs[titindex %in% losers,sum(f * (2 ^ r)),by=titindex]
      losers = losers[V1 == min(losers[,V1]), titindex]
      if (length(losers) > 1) {
        ties = c(dim(fvotes)[1], ties)
      }
    }
    if ((dim(fvotes)[1] - length(losers)) < 5) {
      done = T
    } else {
      ballots[titindex %in% losers, valid:=F]
    }
  }
  
  winners = sort(fvotes[,titindex])
  return(list(rawtie=(nwin > 5),
              ties = ties,
              same = length(intersect(winners, rawWinners)),
              winners = winners,
              rawWinners = rawWinners
              ))
}

stat = function(ballots,orig) {
  sdv = sdvlpe(ballots)
  #if (length(sdv$rawWinners) > 5) {print(sdv$ties)}
  c(sdv$same,length(sdv$winners),length(sdv$rawWinners),sum(sdv$ties < 10))
}

stableStat = function(ballots,orig) {
  sdv = sdvlpe(ballots)
  declined = sample(sdv$winners,1)
  sdv2 = sdvlpe(ballots[,valid:=(titindex != declined)],allValid=F)
  
  #if (length(sdv$rawWinners) > 5) {print(sdv$ties)}
  c(0,length(intersect(sdv$winners,sdv2$winners)))
}



for (i in 1:13) {
  onecat = hugos[cat == i]
  print(sdvlpe(onecat)$ties)
}

n = 600
for (i in 1:13) {
  onecat = hugos[cat == i]
  smaller = hugos[sample(1:dim(hugos)[1],n)]
  boots = boot(onecat,stat, R=100, 
               sim="parametric",
               mle = n
               ,ran.gen=function(d,n){d[sample(1:dim(d)[1],n   ,replace=T)]}#   )]}#,replace=T)]}#
               )
  print(colMeans(boots$t))
}
for (i in 1:13) {
  onecat = hugos[cat == i]
  smaller = hugos[sample(1:dim(hugos)[1],n)]
  boots = boot(onecat,stableStat, R=25, 
               sim="parametric",
               mle = n
               ,ran.gen=function(d,n){d[sample(1:dim(d)[1],n   ,replace=T)]}#   )]}#,replace=T)]}#
               )
  print(colMeans(boots$t))
}


```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)

```

